\documentclass[a4paper,10pt]{report}
\usepackage[utf8]{inputenc}

% Title Page
\title{Technical Report - Train Commander}
\author{
  FREVILLE Titouan \\
  PETRIGNET Julien \\
  \today
}


\begin{document}
\maketitle
\tableofcontents
\begin{abstract}
\end{abstract}

\part{Software Solutions}
  NodeJS or go Solution.
  \chapter{Engine core}
    \section{Provide information to the engine}
      Call sncf api to provide real time data. If nodeJS solution: Ajax Call. If GO solution : go program.
    \section{Find way}
      Process on the data collected in the api using Node or GO function. Function with 3 arguments (Departure, Arrival, Time zone).
    \section{Process reservation}
      Call webview in AngularJS to fulfill the reservation form + make access to a virtual paypal payment.
    \section{Generate PDF bill and ticket}
      Generate the pdf using node or go + send it.
  \chapter{Accounts}
    need a DataBase to store the accompts. Should be a MariaDB or Mysql one (MariaDB is a Mysql "framework").
    \section{Create account}
      \subsection{From mail}
	Classic register form catch by go or node and Process in the database
      \subsection{From Facebook}
	Use Facebook connection api. Store information in the database.
      \subsection{From Google Account}
	Use Google connection api. Store information in the database.
    \section {Review travel}
      Standart call on the database using node or go to read the travel link to the accompt.
    \section{Replicate a previous travel}
      Need to store an historic of the travel from a user in database. Standart call on it to Replicate the valid data.
    \section{Print tickets/receipts}
      Call to the database to confirm he payed ... Standart call to node or go to launch print function (can be a pdf view printed from the navigator).
  \chapter{Access to all feature}
    \section{From website}
      Easy :p Just think about making the reservation process a separate web view who wil be called by the web site.
    \section{From Mobile application}
      Should provide a Android(JAVA) and IOS(Obj. C/swift) application. Think to use the web view for reservation (avoid replication in the work :) )
\part{Supporting Architecture Solutions}
  \chapter{Virtualization}
    \section{Infra to power the app}
      Server should be on a linux system Supporting Vagrant. Call Vagrant to up the virtual machine. The VM should run on coreOS using dockers.
    \section{2 sites}
      Make sure to be able to copy states when the main is forced down.
  \chapter{Cluster}
    \section{Engine}
      Using docker + coreOS + Vagrant as system to run the app, we just have to manage the Cluster in the vagrantfile.
    \section{Web}
      Using docker + coreOS + Vagrant as system to run the app, we just have to manage the Cluster in the vagrantfile.
  \chapter{Web CDN}
    \section{Always pass by CDN}
     Need to find a CDN solution.
    \section{Load balancing}
\end{document}
